Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-02-01 paper/ijcai16.tex
typo

Note that we are choosing the configurations $\{ \vx^i \}$ and the
weight vectors $\{ \vw^i \}$ {\em simultaneously}.  
%Note that the methods bears some similarity with volumetric approaches, but  with important differences. 
We look for $\vw^i$ so that the utility loss (see constraint \ref{eq:wxconstr}) of choosing $\vx^{j}$ instead of $\vx^{i}$, $j \neq i$, is large (at least $\mu$).
Look at
Figure~\ref{fig:setmargin}, where, for simplicity, we need to choose a
pair ($k=2$).  Eq. \ref{eq:wxconstr} is represented by a
red line, that partitions the space of feasible utility weights in two
parts (in general, there will be $k$ subregions).  Since we maximize
the margin $\mu$, the optimizer will prefer a set of configurations
$\{ \vx^{1}, \vx^{2} \}$ that partitions the weight space in an ``even''
way\footnote{This bears similarity with volumetric approaches \cite{iyengar:acm-ec01}, but there are important differences: first here
we consider real items to find the best separator, second the margin is also expressed in utility terms, third the query is found via an optimization process.}. 
In each subregion, we have corresponding %utility weight vector
$\vw^{i}$ lying ``close'' to its centre. 
If, for example, the user indicates a
preference for $\vx^{1}$ over $\vx^{2}$, the feasible region %for the weights 
will then become the part of the polytope to the left of the
red line; moreover the vector $\vw^{1}$ will maximize the margin in the classic ($k=1$) sense in new feasible region.
%Therefore, setwise maxmargin can be thought as a ``look-ahead'' model with respect to a standard ($k=1$) max-margin learner.
%Therefore, setwise maxmargin can be thought as the set that, given any possible preference about the items, ensure that the reduction of utility uncertainty is the greatest
%\paolo{ho fatto un tentativo di migliorare l'intuizione, ma e' ancora possibile migliorare...}

>>>>

Note that we are choosing the configurations $\{ \vx^i \}$ and the
weight vectors $\{ \vw^i \}$ {\em simultaneously}.  
%Note that the methods bears some similarity with volumetric approaches, but  with important differences. 
We look for $\vw^i$ so that the utility loss (see constraint \ref{eq:wxconstr}) of choosing $\vx^{j}$ instead of $\vx^{i}$, $j \neq i$, is large (at least $\mu$).
Look at
Figure~\ref{fig:setmargin}, where, for simplicity, we need to choose a
pair ($k=2$).  Eq. \ref{eq:wxconstr} is represented by a
red line, that partitions the space of feasible utility weights in two
parts (in general, there will be $k$ subregions).  Since we maximize
the margin $\mu$, the optimizer will prefer a set of configurations
$\{ \vx^{1}, \vx^{2} \}$ that partitions the weight space in an ``even''
way.\footnote{This bears similarity with volumetric approaches \cite{iyengar:acm-ec01}, but there are important differences: first here
we consider real items to find the best separator, second the margin is also expressed in utility terms, third the query is found via an optimization process.}
In each subregion, we have corresponding %utility weight vector
$\vw^{i}$ lying ``close'' to its centre. 
If, for example, the user indicates a
preference for $\vx^{1}$ over $\vx^{2}$, the feasible region %for the weights 
will then become the part of the polytope to the left of the
red line; moreover the vector $\vw^{1}$ will maximize the margin in the classic ($k=1$) sense in the new feasible region.
%Therefore, setwise maxmargin can be thought as a ``look-ahead'' model with respect to a standard ($k=1$) max-margin learner.
%Therefore, setwise maxmargin can be thought as the set that, given any possible preference about the items, ensure that the reduction of utility uncertainty is the greatest
%\paolo{ho fatto un tentativo di migliorare l'intuizione, ma e' ancora possibile migliorare...}
